---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# disasteraidr

<!-- badges: start -->
<!-- badges: end -->
## About

The goal of disasteraidr is to have an easy way to download cleaned data in R 
from various sources associated with disaster aid allocation in the UNITED STATES.
This is an ongoing project with the University of Maryland 
Hazards and Infrastructures team. Currently 'cleaned' datasets come 
from HUD, NOAA, and FEMA. The main transformations come in CPI adjustments
and conversion of row details associated with the location to FIPS/county level
resolution. US Territories are left out in some of the dataset such as Guam, Puerto Rico.


## Installation

You can install the development version of disasteraidr from [Github](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("etam4260/disasteraidr")
```

## Example

This is a basic example which shows you how to load in the data:

```{r example}
library(disasteraidr)
# The package currently contains 6 datasets:
# These will return <promise> objects. If in R studio, click on
# the <promise> tag to load it in.

# FEMA Hazard Mitigation Assistance Projects
data("hma")

# NOAA Storm Events
data("noaastorm")

# FEMA Individuals and Household Programs
data("ihp")

# HUD Community Block Grant Program
data("cdbgdr")

# FEMA Public Assistance
data("pa")

# FEMA Disaster Declarations
data("dd")
```
